---
title: "Homework 1"
author: "Yiyu Zhou"
date: "September, 2023"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

# A little bit about myself

a. Why am I interested in taking this course?

    After years of programming, I want to switch my gear a little bit and
    discover some new things that are very closely related to what I've been
    doing but which I have never done before, that is Data Science.

b. Have I ever used R before this course? If so, to what extent?

    I have never used R before, and all I have heard about R is that it's part
    of the GNU project.

c. Have I ever used another programming language before? How would I rate my
skill level?

    I have used C, RISC-V Assembly, Java, C#, Python, JavaScript, Lisp (Emacs
    Lisp), Vimscript/VimL, Bash and Lua. I have extensive knowledge with C and
    GNU toolchain.

d. What major am I? What do I plan on doing when you graduate from USF?

    I'm a Computer Science major. I plan to graduate from USF at 2026.

e. Things that I hope to do with R this semester.

    I hope to learn how to analyze data using R this semester.

f. Something interesting I want to share.

    I was telling you earlier about this project called
    [glow](https://github.com/charmbracelet/glow), it gives you the ability to
    render Markdown in the terminal emulator. It is very cool because before you
    commit a change to a Markdown file, you can preview the visual effects of it
    right in the terminal.

# Chapter 1 of *Doing Data Science*: [What is Data Science?](https://www.oreilly.com/library/view/doing-data-science/9781449363871/ch01.html)

a. From reading the article, what in your opinion is the biggest issue facing
the field of “data science,” and what do you think can be done to help fix this
issue?

    From reading the article, I think the biggest issue facing the field of
    "data science" is the lack of understanding on the subject. Due to people
    not fully knowing what data science is, there is also a lack of respect for
    the people working within the industry of data science. Many people believe
    it to be a new concept but Big Data and the field of data science have been
    around for a very long time and are built upon everything that has come
    before with work from statisticians, computer scientists, mathematicians to
    name a few. I think more education on the history and field of data science
    would be very helpful in expanding the repect and understanding for all the
    work being done.

b. What, in your opinion, is the biggest difference between traditional
statistics and data science? How does technology play a role in this difference?

    In my opinion, the biggest difference between traditional statistics and
    data science is how we handle the data. For statisticians, their main goal
    is hypothesis testing on data whereas for data scientists, they are more
    focused on finding patterns and building models from data. Data science is
    also an interdisciplinary study combining computer science, statistics,
    communication, data visualization and much more.

c. What, in your opinion, is the biggest difference between data scientists in
academia and industry?

    In academia, there are no data scientists. At least none who refer to
    themselves as such within academia. Data scientists in academia
    focus on advancing research whether that be through publishing papers,
    securing research funding, or presenting their knowledge. The definition of
    research within data science is a gray area and must be defined more
    formally for the idea of a data scientist in academia to progress.
    In industry, a data scientist uses data to provide actionable business
    value whether that be through increasing revenue, reducing costs, or
    improving the user experience. Data scientists in industry often measure
    their success through the tangible impact their work has on a commpany or
    consumer.

b. What kind of data scientist do you want to be? What skills are you most
interested in developing?

    I want to be a data scientist who focuses on security of systems. I am most
    interested in strengthening my skills with the R language and better
    understanding how to use data to make impactful technologies for users.

c. Based on this article, a major obstacle in understanding data science in the
first place is understanding what data science actually is. From what you’ve
read, and what you understand so far, how would **you** define the term
“data science”?

    I would define data science as a blend of technology and mathematics. It
    combines the hypothesizing of data and programming to utilize the data. The
    data is used for many different purposes ranging from decision making to
    developing new technologies and data scientists play a huge role within all
    of it as well as computer scientists and mathematicians. Data science can be
    applied in nearly every industry.

# Calculations

Here are some examples of calculations in R.

a. assignment

    ```{r, eval = TRUE, echo = TRUE}
    x <- 3
    y <- 4
    ```

b. $\ln(x+y)$

    ```{r, eval = TRUE, echo = TRUE}
    log(x + y)
    ```

c. $\log_{10}(\frac{xy}{2})$

    ```{r, eval = TRUE, echo = TRUE}
    log(x * y / 2)
    ```

d. $2x^\frac{1}{3} + y^\frac{1}{4}$

    ```{r, eval = TRUE, echo = TRUE}
    2 * x ^ (1 / 3) + y ^ (1 / 4)
    ```

e. $10^{x-y} + e^{xy}$

    ```{r, eval = TRUE, echo = TRUE}
    e <- exp(1)
    10 ^ (x - y) + e ^ (x * y)
    ```

# What does `M-K` do in RStudio?

In RStudio, pressing `M-K` (`Alt + Shift + K`) brings up the `Keyboard Shortcut
Quick Reference`. Another way to access RStudio keyboard shortcuts is with the
menu entry: `Tools > Keyboard Shortcuts Help`.

# What is "Big Data"?
Big Data refers to extremely large data sets that are beyond the capability of
traditional databases and data processing systems to capture, store, manage, and
analyze. These data sets can be structured (like databases), semi-structured
(like JSON or XML files), or unstructured (like text documents or images).
